\subsection{Achieve[AccurateAmbulancePositionRecordedWhenAccurateAmbulancePositionSent]}

The accurate position of the ambulance is eventually recorded in the system when ambulance position is sent.


\subsection{Achieve[AccurateAmbulancePositionSent]}

The accurate position of the ambulance is eventually sent.


\subsection{Achieve[AmbulanceChosen]}

The best ambulance is eventually chosen. The best ambulance is the available ambulance of the right kind which may arrive quickly on the scene.


\subsection{Achieve[AmbulanceChosenWhenIncidentInfoKnown]}

All available ambulances of the right kind are eventually chosen.


\subsection{Achieve[AmbulanceMobilizedWhenIncidentInfoKnown]}

Once the information about the incident are known, the right ambulance and his crew are eventually mobilized.


\subsection{Achieve[AmbulanceOnSceneWhenAmbulanceMobilized]}

Ambulance eventually arrived on the scene when the ambulance is mobilized by the system.


\subsection{Achieve[AppropriateMedicalCareAreGivenQuickly]}

According to the standard, appropriate medical care are given quickly. An ambulance must arrive at the scene within 14 of the call commencing on 95\% of occasion. An ambulance must arrive at the scene within 8 minutes of the call commencing on 50\% of occasions.


\subsection{Achieve[AppropriateMedicalCareGivenWhenAmbulanceMobilized]}

Once the ambulance is mobilized, ambulance crew  give eventually the appropriate medical care to the victim.


\subsection{Achieve[AppropriateMedicalCareGivenWhenAmbulanceOnScene]}

The appropriate medical care are eventually given to the victim by the ambulance crew once the ambulance arrived on scene.


\subsection{Achieve[AppropriateMedicalCareGivenWhenCallReceived]}

For every call received the appropriate medical care are given to the victim taking in account the time constraints


\subsection{Achieve[AppropriateMedicalCareGivenWhenInjuredPeople]}

Every injured people receive the appropriate medical care that he need


\subsection{Achieve[CallReceivedWhenInjuredPeople]}

For every injured people who need medical care, a call is received by the call center.


\subsection{Achieve[IncidentInfoKnownWhenCallReceived]}

For every call received all needed information about the incident are eventually known by the system.


\subsection{Achieve[IncidentInfoProcessedWhenIncidentInfoRecorded]}

Information about the incident are eventually processed (e.g. the avls coordinates are computed and incident gravity is defined) when the information about the incident are recorded in the system.


\subsection{Achieve[IncidentInfoRecordedWhenCallReceived]}

The information about the incident are eventually recorded in the system when the call is received by the call center.


\subsection{Achieve[MobilisationOrderConfirmedWhenMobilisationOrderTransmitted]}

Ambulance crew eventually confirmed mobilisation after order transmission.


\subsection{Achieve[MobilizationOrderConfirmedByAmbulanceCrewWhenMobilizationOrderDisplayed]}

When the mobilization order is displayed on the MDT, it is eventually confirmed by the ambulance crew.
 

\subsection{Achieve[MobilizationOrderConfirmedWhenMobilizationOrderConfirmedByAmbulanceCrew]}

When the ambulance crew confirmed the mobilization order, the confirmation is eventually confirmed to the system. 


\subsection{Achieve[MobilizationOrderDisplayedWhenMobilizatedOrderTransmitted]}

When mobilization order is transmitted, it is eventually displayed on the MDT.
 

\subsection{Achieve[MobilizationOrderReadWhenMobilizationOrderDisplayed]}

The mobilization order sent by the system to the ambulance crew is eventually read by the ambulance crew.


\subsection{Achieve[MobilizationOrderReceivedWhenMobilizationOrderSent]}

The mobilization order is eventually received when it was sent from the system.


\subsection{Achieve[MobilizationOrderSentWhenBestAmbulanceChosen]}

The mobilization order is eventually sent when the best ambulance has been choosen.


\subsection{Achieve[MobilizationOrderTransmittedWhenAmbulanceChosen]}

The mobilization order is enventually transmitted to the ambulance crew when the best ambulance is chosen


\subsection{AmbulanceMobilizedWhenMobilizationOrderConfirmed}

When the mobilization order is confirmed to the system, the ambulance is considered as mobilized. 


\subsection{AmbulancePositionKnownWhenAmbulancePositionRecorded}

The position of an ambulance is known when the ambulance position is recorded in the system.


\subsection{IncidentInfoKnownWhenProcessed}

The incident information are known when the incident information are processed by the system.


\subsection{Maintain[AmbulanceAvailabilityKnown]}

The ambulance availability is always known by the system.


\subsection{Maintain[AmbulanceKindKnown]}

The kind of the ambulance is always known by the system.


\subsection{Maintain[AmbulancePositionKnownAndAccurate]}

The ambulance position is always known by the system.


\subsection{Maintain[HighSystemReliability]}

The system is sufficantly reliable.
 

\subsection{Maintain[HighSystemUsability]}

The system is sufficantly usable.

 

\subsection{Maintain[LowEnvironmentalImpact]}
 
The system has a low environmental impact.


\subsection{Maintain[LowSystemCosts]}

System costs are low.
 

\subsection{MobilisationOrderTransmittedWhenMobilisationOrderRecieved}

The mobilization order is considered as transmitted when the mobilization order was received by the ambulance crew.
